PoolTestRPaper

### 2020-09-17 paper/Paper.Rmd
reordered arguments in Regression functions to match R standards
Also allowed users to specify custom priors with PoolRegBayes

---
title: "PoolTestRPaper"
author: "AngusMcLure"
date: "05/06/2020"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen]

We wish to estimate the prevalence, p, of a disease or molecular marker in a population from the results of tests on a pooled samples. For a pool combining N samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$. If $M$ such pools from a single location are tested and $m$ of these are positive the maximum likelihood estimate (MLE) of $q\ is \frac{m}{M}$ and the MLE of the prevalence, $p$, in the population is ${1-\left(1-\frac{m}{M}\right)}^\frac{1}{N}$. However, if the pools are of different sizes there is no convenient closed-form expression for the MLE, which must be approximated numerically from the likelihood function. With pools of size $N_1,N_2,\ldots$, and tests results $y_1,y_2,\ldots$ (where $y_i$ is zero if the test result is negative and one if positive) the likelihood function is

@@

 `PoolReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for fixed effects models and builds on the `glmer` function from the `lme4` package for mixed effect models. `PoolRegBayes` builds on the flexible non-linear modelling framework provided by the `brms` package to fit bayesian fixed and mixed effect regression models on data from pooled tests. By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of R.

@@

The boxes below demonstrated the use of `PoolPrev` on a synthetic dataset. The synthetic dataset consists of 1000 pools from four different locations (A-D) over five years (0-4) of sampling. The ‘true’ prevalence in the initial year was 14% in locations A and D, 4% in location B and 1% in location C, and declined by approximately 18% each year.

```{r GenerateDataset, include=FALSE}
library(dplyr)
library(tidyr)
### Create a synthetic dataset with 4 locations across 5 years,
### where prevalence is declining
NumPools <- 1000
#Odds that a individual sample is positive in each location in the first year
BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
OddsRatioYear <- 0.8
#Randomly distribute pools between the 4 locations and 5 years,
#and chose random pool sizes between 10 and 25
Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
                   Year = sample(c(0:4), NumPools, replace = T),
                   NumInPool = sample(10:25, NumPools, replace = T))
#'True' odds/prevalence in each location
Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
#Simulate test results on pools
Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
Data <- Data %>% select(-TrueOdds,-TruePrev)
```

```{r PoolPrevExample}
#Looking at the first few rows of the synthetic dataset to see structure
head(Data)
#Prevalence across the whole synthetic dataset
PoolPrev(Data, Result,NumInPool)
#Prevalence at each location
PoolPrev(Data, Result,NumInPool,Place)
#Prevalence for each Year
PoolPrev(Data, Result,NumInPool,Year)
#Prevalence for each combination of location and Year
PoolPrev(Data, Result,NumInPool,Place,Year)
```

### PoolLogitReg
Given a dataset containing the number of samples, the result of tests for each pool, potential dependent variables associated with each pool, and a formula defining the model, `PoolLogitReg` fits a logistic regression model that adjusts for the sizes of pools. The output is a S3-object of class `glm` which supports that same methods (e.g. summary, predict, plot, confint) as any other object returned by the `glm` function.

The boxes below apply `PoolLogitReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.

```{r PoolLogitRegExample}
# Fit modified logistic regression model
#The below two lines produce identical results and support all the same methods
Reg <- PoolReg(Data,Result ~ Place + Year,
                    NumInPool)
Reg.glm <- glm(Result ~ Place + Year,
               data = Data,
               family = binomial(PoolLink(Data$NumInPool)))
#View summary of model
summary(Reg)

@@

Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolReg`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location. Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
```{r Comparison, echo=FALSE}
library(ggplot2)
PrevsYearPlace <- PoolPrev(Data, Result,NumInPool,Place,Year)
PO <- PrevsYearPlace %>%
  mutate(BaseOdds = BaseOdds[Place],
         TrueOdds = BaseOdds * OddsRatioYear^(Year-min(Year)),
         TruePrev = TrueOdds/(1+TrueOdds),
         FreqPred = plogis(predict(Reg,newdata = PrevsYearPlace)),
         FreqPredCILow = with(predict(Reg,
                                      newdata = PrevsYearPlace,
                                      se.fit =T),
                              fit - se.fit * 1.96) %>% plogis,
         FreqPredCIHigh = with(predict(Reg,
                                       newdata = PrevsYearPlace,
                                       se.fit =T),
                               fit + se.fit * 1.96) %>% plogis
  ) %>%
  ggplot() +
  geom_pointrange(aes(x = Year,
                      color = Place,
                      y = PrevMLE,
                      ymin = CILow,
                      ymax = CIHigh)) +
  geom_line(aes(x = Year,
                y= FreqPred,
                color = Place)) +
  geom_ribbon(aes(x = Year,
                  ymin = FreqPredCILow,
                  ymax = FreqPredCIHigh,
                  fill = Place),
              alpha = 0.3) +
  geom_point(aes(x = Year, color = Place, y = TruePrev),
             shape = 4,
             size = 3) +
  #scale_y_log10() +
  ylab('Prevalence')
PO
```

## Testing
A more realistic example:
- 3 regions with prevalence:
  - low (0.5%)
  - medium (2%)
  - high (4%) 
- 10 villages in each region with prevalence:
  - random normal distribted tight around region average, or 
  - one hotspot and one coldspot village
- 15 sites at each village.
  - Mosquitos caught at each site is random from normal/lognormal distribution so that 0 and 500 and both rare
  - Mosquitos pooled into test-tubes of 25 + one pool with remainder

```{r GenerateMoreRealisticDataset}
RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
NumRegions <- length(RegionPrevs)
NumVillages <- 10 #Villages per Region
NumSites <- 15 #Sites per village
MeanCatch <- 200; #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
DispersionCatch <- 5
MaxPoolSize <- 25
# Variability between villages and between sites in a given village.
# We could probably increase these standard deviations to make the difference between the hierarchical and non-hierarchical models more stark
VillageSD <- 1.0 
SiteSD <- 0.5

Data <- data.frame()
for(R in names(RegionPrevs)){
  for(V in 1:NumVillages){
    #Difference of village prevalence from the region prevalence on log-odds scale
    VillageDeviate <- rnorm(1,mean = 0, sd = VillageSD)
    VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate)
    for(S in 1:NumSites){
      #Difference of site prevalence from the village prevalence on log-odds scale
      SiteDeviate <- rnorm(1,mean = 0, sd = SiteSD)
      SiteTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + SiteDeviate)
      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes == 0 to guarantee at least one mossie
      Catch <- 0
      while(Catch<=0){
        Catch <- rnbinom(1,mu = MeanCatch ,DispersionCatch)
      }
      #Split pools into as many of size MaxPoolSize as possible and the remainder in another small pool
      NumBigPools <- Catch %/% MaxPoolSize
      if(NumBigPools){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = rep(MaxPoolSize,NumBigPools),
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }
      SizeSmallPool <- Catch %% MaxPoolSize
      if(SizeSmallPool){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = SizeSmallPool,
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }
    }
  }
}
Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < (1-(1-PrevalenceSite)^PoolSize)))

# Calculating prevalences at different levels ignoring hierarchical sampling structure
PrevRegion <- PoolPrev(Data,Result,PoolSize,Region)
PrevVillage <- PoolPrev(Data,Result,PoolSize,Region,Village)
PrevSite <- PoolPrev(Data,Result,PoolSize,Region,Village,Site)

# Calulcating prevalences at different levels acknowledging hierarchical structure

# Similar to above but in a regresison framework with Region as population
# effect (aka fixed effect) and Village and Site as group effects (aka random
# effect)

HierPrevModel <- PoolRegBayes(Data, Result ~ Region + (1|Village/Site), PoolSize)
HierPrevs <- getPrevalence(HierPrevModel) # Gett fitted prevalence at each level: Population Effects only (in this case this is region), Population Effects and Village, and population effects, village and site.

```{r HierComparisonRegion, echo=FALSE}
PlotDataRegion <- PrevRegion %>%
  unique %>%
  select(Region, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevRegion %>%
              unique %>%
              select(Region, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region,PrevalenceRegion) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceRegion)) %>%
  bind_rows(HierPrevs$PopulationEffects %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Prev, CILow, CIHigh, Method))

@@

```
```{r HierComparisonVillage, echo=FALSE}
PlotDataVillage <- PrevVillage %>%
  unique %>%
  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevVillage %>%
              unique %>%
              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region, Village,PrevalenceVillage) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceVillage)) %>%
  bind_rows(HierPrevs$Village %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
  subset(VillageNum %in% 1:5)

>>>>

---
title: "PoolTestRPaper"
author: "AngusMcLure"
date: "05/06/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.extra = R.version.string)
knitr::opts_chunk$set(cache.extra = R.version)
library(PoolTestR)
```

[Some one or two line sentence preamble with references to the literature? E.g. the papers associated with pool screen.[^2] ]

[^2]: We need to also talk about the existing R packages BinGroup and BinGroup2. Perhaps we can sell ourselves as offerring a more user-friendly approach?
Can we make a shiny app which uses our package as the backend where people can upload their data?
Also, we introduce heirarchical models (which they don't?)
Also, we include by default Bayesian version (which they don't?)
Also, we can calculate confidence intervals for any number of group sizes (which they can but only very slowly?)
This website has a lot of work on group testing (he seems to have built his career around group-testing!) http://www.chrisbilder.com/grouptesting/

We wish to estimate the prevalence, $p$, of a disease or molecular marker in a population from the results of tests on a pooled samples. For a pool combining $N$ samples, if we assume that the probability of having the marker is independent across specimens with and between pools, that the sample size is much smaller than the population, and that the test has perfect sensitivity and specificity, the probability $q$ of returning a positive test result is $q=\ 1-\left(1-p\right)^N$. If $M$ such pools from a single location are tested and $m$ of these are positive the maximum likelihood estimate (MLE) of $q\ is \frac{m}{M}$ and the MLE of the prevalence, $p$, in the population is ${1-\left(1-\frac{m}{M}\right)}^\frac{1}{N}$. However, if the pools are of different sizes there is no convenient closed-form expression for the MLE, which must be approximated numerically from the likelihood function. With pools of size $N_1,N_2,\ldots$, and tests results $y_1,y_2,\ldots$ (where $y_i$ is zero if the test result is negative and one if positive) the likelihood function is

@@

 `PoolReg` builds on the generalized linear modelling function, `glm`, from the in the `stats` package for fixed effects models and builds on the `glmer` function from the `lme4` package for mixed effect models. `PoolRegBayes` builds on the flexible non-linear modelling framework provided by the `brms` package to fit bayesian fixed and mixed effect regression models on data from pooled tests. By building on these existing packages, `PoolTestR` leverages the extensive suite of diagnostics tools available for working with models fitted with these functions and uses paradigms that will be familiar to existing users of `R`.

@@

The boxes below demonstrate the use of `PoolPrev` on a synthetic dataset. The synthetic dataset consists of 1000 pools from four different locations (A-D) over five years (0-4) of sampling. The ‘true’ prevalence in the initial year was 14% in locations A and D, 4% in location B and 1% in location C, and declined by approximately 18% each year.

```{r GenerateDataset, include=FALSE, cache=TRUE}
library(dplyr)
library(tidyr)
### Create a synthetic dataset with 4 locations across 5 years,
### where prevalence is declining
NumPools <- 1000
#Odds that a individual sample is positive in each location in the first year
BaseOdds <- c(A = 0.16, B = 0.04, C = 0.01, D = 0.16)
OddsRatioYear <- 0.8
#Randomly distribute pools between the 4 locations and 5 years,
#and chose random pool sizes between 10 and 25
Data <- data.frame(Place = sample(c("A","B","C","D"),NumPools, replace = T),
                   Year = sample(c(0:4), NumPools, replace = T),
                   NumInPool = sample(10:25, NumPools, replace = T))
#'True' odds/prevalence in each location
Data$TrueOdds <- with(Data,BaseOdds[Place] * OddsRatioYear^(Year-min(Year)))
Data$TruePrev <- with(Data, TrueOdds/(1+TrueOdds))
#Simulate test results on pools
Data$Result <- with(Data,as.numeric(runif(NumPools) < 1-(1-TruePrev)^NumInPool))
Data <- Data %>% select(-TrueOdds,-TruePrev)
```

```{r PoolPrevExample, warning=FALSE, cache=TRUE}
#Looking at the first few rows of the synthetic dataset to see structure
head(Data)
#Prevalence across the whole synthetic dataset
PoolPrev(Data, Result,NumInPool)
#Prevalence at each location
PoolPrev(Data, Result,NumInPool,Place)
#Prevalence for each Year
PoolPrev(Data, Result,NumInPool,Year)
#Prevalence for each combination of location and Year
PoolPrev(Data, Result,NumInPool,Place,Year)
```

### Regression
Our package provides tools for mixed-effect regression models in both a frequentist and Bayesian framework. `PoolReg` fits a frequentist mixed- or fixed-effect logistic regression model that adjusts for the sizes of pools. For a model with only fixed effects the output is a S3-object of class `glm`, while the output for a model with random effects is a S3-object of class 'glmerMod' which supports that same methods (e.g. summary, predict, plot, confint) as any other object returned by the `glm` or `glmer` functions. `PoolRegBayes` provides functionality to perform the same analyses in a Bayesian framework.

The boxes below apply `PoolReg` to the same synthetic dataset used to demonstrate `PoolPrev`, correctly identifying that locations A and D have the same prevalence, and estimating the rate of decline in prevalence over time.

```{r PoolLogitRegExample, warning=FALSE, cache=TRUE}
# Fit modified logistic regression model
#The below two lines produce identical results and support all the same methods
Reg <- PoolReg(Result ~ Place + Year, Data, NumInPool)
Reg.glm <- glm(Result ~ Place + Year,
               data = Data,
               family = binomial(PoolLink(Data$NumInPool)))
#View summary of model
summary(Reg)

@@

Figure 1 compares the prevalence estimates based on the modified logisitic model (`PoolReg`), estimates based on each time and place independently (`PoolPrev`) and the 'true' prevalence at each location. Note that while both methods produce good estimates with the true values falling within confidence intervals, the modified logistic regression model has tigher confidence intervals.
```{r Comparison, echo=FALSE, warning=FALSE}
library(ggplot2)
PrevsYearPlace <- PoolPrev(Data, Result,NumInPool,Place,Year)
PO <- PrevsYearPlace %>%
  mutate(BaseOdds = BaseOdds[Place],
         TrueOdds = BaseOdds * OddsRatioYear^(Year-min(Year)),
         TruePrev = TrueOdds/(1+TrueOdds),
         FreqPred = plogis(predict(Reg,newdata = PrevsYearPlace)),
         FreqPredCILow = with(predict(Reg,
                                      newdata = PrevsYearPlace,
                                      se.fit =T),
                              fit - se.fit * 1.96) %>% plogis,
         FreqPredCIHigh = with(predict(Reg,
                                       newdata = PrevsYearPlace,
                                       se.fit =T),
                               fit + se.fit * 1.96) %>% plogis
  ) %>%
  ggplot() +
  geom_pointrange(aes(x = Year,
                      color = Place,
                      y = PrevMLE,
                      ymin = CILow,
                      ymax = CIHigh)) +
  geom_line(aes(x = Year,
                y= FreqPred,
                color = Place)) +
  geom_ribbon(aes(x = Year,
                  ymin = FreqPredCILow,
                  ymax = FreqPredCIHigh,
                  fill = Place),
              alpha = 0.3) +
  geom_point(aes(x = Year, color = Place, y = TruePrev),
             shape = 4,
             size = 3) +
  #scale_y_log10() +
  ylab('Prevalence')
PO
```

## Hierarchical Sampling Structure
Many xenomonitoring surveys involve a hierarchical sampling structure. For instance if one wishes to understand the prevalence in a particular village, one may place traps at a number of sites around the village. The vectors caught at each site can then be tested individually or in pools. However, as prevalence may vary from site to site, the result of tests on individuals vectors or pools from the same site cannot be considered independent. However, the function `PoolPrev` in our package and other software like PoolScreen assume that results of pools are independent. Estimating the prevalence for the whole village ignoring this dependance will result in over-confident (narrow) estiamtion intervals. To account for this dependance we can use a hierarchical model. [^3]

[^3]: Should we make some note about an alternate appraoch? i.e. If prevalence is not expected to vary much between sites and the number of vectors caught at each site are similar, one can combine the vectors trapped across the whole village and create pools from this common set of specimens. However, this may mask any variation between sites, discarding potentially useful spatial information. Our package provides two ways of accounting for hierarchy in the sampling frame.

`HeirPoolPrev` fits an intercept-only hierarchical model. The syntax and outputs are very similar to `PoolPrev`. There is only one additional argument, `hierarchy`, describing the hierachical structure of the sampling frame. The output provides the Bayesian posterior mean and credible intervals for the prevalence, but unlike `PoolPrev` does not provide the maximum-likelihood estimate or likelihood ratio confidence intervals [^4]. As with `PoolPrev` users can specify variables that split the dataset into subgroups. If subgroups of the data are specified, estimation proceeds independantly for each subgroup.

A more flexible modelling approach is provided by the regression functions `PoolReg` and `PoolRegBayes` which can account for hierarchical sampling structure as random-effects or group-effects. The function `getPrevalence` provides a convenient way of extracting predicted prevalences and confidence intervals at each level of the sampling frame.

We illustrate both approaches with another synthetic dataset with a realistic hierarchical sampling frame. We simulate samples taken from across three regions (A, B, and C) in which the vectors have a low (0.5\%), medium (2\%), and high (4\%) prevalence of the marker of interest. Within each region we choose ten villages, and within each of these villages we choose fifteen sites to place traps. Within each region prevalence varies between villages around the mean for the region, and within each village prevalence varies between sites around the mean for the village. A zero-truncated negative binomial number (mean 200, dispersion 5) of vectors are caught at each site. The catch size at each site is independent. The catches at each site are pooled into groups of 25 with an additional pool for any remainder (e.g. a catch of 53 vectors will be pooled into two pools of 25 and one pool of three). The test is assumed to have perfect sensitivity and specificity.

[^4]: We could provide frequentist outputs too (MLE estimate and confidence intervals), but the confidence intervals get pretty tricky so I'd use bootstrapping which is just as slow as Bayesian analysis. I'm not sure there's much utility to this. `PoolPrev` has the frequentist options because that's what people who've used PoolScreen might expect (and it's easy). However, `HierPoolPrev` already departs from PoolScreen so people shouldn't have the same expectations. Besides, frequentist methods might be unstable or non-sensicle when all the pools from one of the sites are positive or negative

```{r GenerateMoreRealisticDataset, include=FALSE, cache=TRUE}
RegionPrevs <- c(A = 0.5, B = 2, C = 4)/100 #Prevalence in each region
NumRegions <- length(RegionPrevs)
NumVillages <- 10 #Villages per Region
NumSites <- 15 #Sites per village
MeanCatch <- 200; #Mean and dispersion of mosquito catch sizes (neg binomial distributed)
DispersionCatch <- 5
MaxPoolSize <- 25
# Variability between villages and between sites in a given village.
# We could probably increase these standard deviations to make the difference between the hierarchical and non-hierarchical models more stark
VillageSD <- 1.0 
SiteSD <- 0.5

Data <- data.frame()
for(R in names(RegionPrevs)){
  for(V in 1:NumVillages){
    #Difference of village prevalence from the region prevalence on log-odds scale
    VillageDeviate <- rnorm(1,mean = 0, sd = VillageSD)
    VillageTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate)
    for(S in 1:NumSites){
      #Difference of site prevalence from the village prevalence on log-odds scale
      SiteDeviate <- rnorm(1,mean = 0, sd = SiteSD)
      SiteTruePrev <- plogis(qlogis(RegionPrevs[[R]]) + VillageDeviate + SiteDeviate)
      #Generate catch sizes from zero-truncated negative binomial distribution. 're-roll' sizes == 0 to guarantee at least one mossie
      Catch <- 0
      while(Catch<=0){
        Catch <- rnbinom(1,mu = MeanCatch ,DispersionCatch)
      }
      #Split pools into as many of size MaxPoolSize as possible and the remainder in another small pool
      NumBigPools <- Catch %/% MaxPoolSize
      if(NumBigPools){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = rep(MaxPoolSize,NumBigPools),
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }
      SizeSmallPool <- Catch %% MaxPoolSize
      if(SizeSmallPool){
        Data <- rbind(Data,
                      data.frame(Region = R,
                                 Village = paste(R,V,sep = "-"),
                                 Site = paste(R,V,S,sep = "-"),
                                 PoolSize = SizeSmallPool,
                                 PrevalenceSite = SiteTruePrev,
                                 PrevalenceVillage = VillageTruePrev,
                                 PrevalenceRegion = RegionPrevs[[R]]))
      }
    }
  }
}
Data$Result <- with(Data,as.numeric(runif(nrow(Data)) < (1-(1-PrevalenceSite)^PoolSize)))
```
```{r HierarchicalPrevalence, warning=FALSE, cache=TRUE}
# Calculating prevalences for each region ignoring hierarchical sampling frame
PrevRegion <- PoolPrev(Data, Result, PoolSize, Region)
# Calculating prevalences for each region acknowledging the hierarchical sampling frame
PrevRegionHier <- HierPoolPrev(Data, Result, PoolSize, c('Site','Village'), Region)

# Similar to above but in a more flexible mixed-effect regresison framework.
# Here we treat region as a population effect (aka fixed effect) and Village and
# Site as group effects (aka random effects). If we had additional covariates
# (e.g. socio-geographic characteristics of each site or villages) we could also
# include these as population effects

# Fit a Bayesian model
HierPrevModel <- PoolRegBayes(Result ~ Region + (1|Village/Site), Data, PoolSize)
# Extracting  prevalence at each level from the fitted model. The output is a list with three entries:
#     Prevalence for each combination of population effects (in this case this is region)
#     Prevalence for each Village within each region
#     Prevalence for each site within each village and region
HierPrevs <- getPrevalence(HierPrevModel) 
head(HierPrevs)

# Should we do the same thing but in a frequentist framework? We could get confidence intervals using bootMer? This is slower even than Bayesian inference, so I would always use (and suggest people use) the Bayesian version anyway. I have not implemented getPrevalence for the frequentist model yet, but it shouldn't be too hard if want to provide it as an option
HierPrevModelFreq <- PoolReg(Result ~ Region + (1|Village/Site), Data, PoolSize)
```

```{r HierComparisonRegion, echo=FALSE,warning = FALSE}
PlotDataRegion <- PrevRegion %>%
  unique %>%
  select(Region, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevRegion %>%
              unique %>%
              select(Region, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region,PrevalenceRegion) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceRegion)) %>%
  bind_rows(HierPrevs$PopulationEffects %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Prev, CILow, CIHigh, Method))

@@

```
```{r HierComparisonVillage, echo=FALSE, warning = FALSE}
PlotDataVillage <- PrevVillage %>%
  unique %>%
  select(Region, Village, PrevMLE, CILow, CIHigh) %>%
  mutate(Method = 'Basic MLE') %>%
  rename(Prev = PrevMLE) %>%
  bind_rows(PrevVillage %>%
              unique %>%
              select(Region, Village, PrevBayes, CrILow, CrIHigh) %>%
              mutate(Method = 'Basic Bayes') %>%
              rename(Prev = PrevBayes,
                     CILow= CrILow,
                     CIHigh = CrIHigh)) %>%
  bind_rows(Data %>%
              select(Region, Village,PrevalenceVillage) %>%
              unique %>%
              mutate(Method = "True") %>%
              rename(Prev = PrevalenceVillage)) %>%
  bind_rows(HierPrevs$Village %>%
              mutate(Method = 'Heirarchical Bayes') %>%
              rename(Prev = Estimate,
                     CILow = CrILow,
                     CIHigh = CrIHigh) %>%
              select(Region, Village, Prev, CILow, CIHigh, Method)) %>%
    mutate(VillageNum = (strsplit(as.character(Village),"-") %>% as.data.frame() %>% t)[,2] %>% as.integer) %>%
  subset(VillageNum %in% 1:5)
